---
title: "Home"
output:
  html_document:
    toc: false
---

## Run ANNOVAR


## From VCF file to individual genotype matrix 

In some cases, the individual genotype matrix is needed for subsequent analysis, say run SKAT from [VCF file](https://samtools.github.io/hts-specs/VCFv4.2.pdf).

```{r, echo=T, eval=F}
library(vcfR)
vcf=read.vcfR("/Users/han24/Documents/Research/rare-var/AutismDbGaP/73416-DS-ASD/pseudocc.tucc.vcf.gz.1.to.500000.gz")
## read.vcfR couldn't load this large file 
```


## Run SKAT on plink bed file 

bed,bim and fam files are produced by plink. SetID  is created from variant_function, one output of annovar. 


```{r, echo=T, eval=F}
## firs several rows of c1.avinput.variant_function
ncRNA_exonic	DDX11L1	1	12198	12198	G	C	.	2955.57	.
ncRNA_intronic	DDX11L1	1	12266	12266	G	A	.	763.37	.
ncRNA_intronic	DDX11L1	1	12272	12272	G	A	.	766.9	.
ncRNA_intronic	DDX11L1	1	12559	12559	G	A	.	184.16	.
ncRNA_intronic	DDX11L1	1	12597	12597	T	C	.	39.93	.

## to create SetID file, the second and fourth columns are used as its first and second column.  
```


```{r, echo=T, eval=F}
library(SKAT)

Generate_SSD_SetID("/project2/xinhe/Shengtong/ASD_dbGaP_032020/data_from_nick/73416-DS-ASD/pseudocc.tucc.bed", 
                   "/project2/xinhe/Shengtong/ASD_dbGaP_032020/data_from_nick/73416-DS-ASD/pseudocc.tucc.bim", 
                   "/project2/xinhe/Shengtong/ASD_dbGaP_032020/data_from_nick/73416-DS-ASD/pseudocc.tucc.fam", 
                   "/project2/xinhe/Shengtong/ASD_dbGaP_032020/data_from_nick/73416-DS-ASD/c1.avinput.variant_function.NoDuplicate.1-1000.setID", 
                   "/project2/xinhe/Shengtong/ASD_dbGaP_032020/data_from_nick/73416-DS-ASD/File.SSD", 
                   "/project2/xinhe/Shengtong/ASD_dbGaP_032020/data_from_nick/73416-DS-ASD/File.Info")
## SetID must not have duplicates 
## File.SSD and File.Info are output file. 

FAM<-Read_Plink_FAM("/project2/xinhe/Shengtong/ASD_dbGaP_032020/data_from_nick/73416-DS-ASD/pseudocc.tucc.fam", Is.binary=FALSE)
y<-FAM$Phenotype
SSD.INFO<-Open_SSD("/project2/xinhe/Shengtong/ASD_dbGaP_032020/data_from_nick/73416-DS-ASD/File.SSD", 
                   "/project2/xinhe/Shengtong/ASD_dbGaP_032020/data_from_nick/73416-DS-ASD/File.Info")
```

*  [Genomic Annotation](GenomicAnnotations.html) is here. 
*  Easier to deploy the website with Git and GitHub by only using one branch

[rmarkdown]: http://rmarkdown.rstudio.com/rmarkdown_websites.htm
[rstudio]: https://www.rstudio.com/products/rstudio/download/preview/
